Supplementary Information

### 2021-01-06 doc/manuscript/MEE_manuscript.Rmd
update interactions results

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Dec.24)
n_DBHx_analyzed=219
n_DBHx_analyzed_sig=82
#precip:
n_DBHxP_RW_analyzed= 38
n_DBHxP_RW_sig=13
n_DBHxP_RW_sig_pos=13-3 #(exceptions: BEAL & TSCA at HF, AFXY at HKK)
n_DBHxP_BAI_analyzed= 38
n_DBHxP_BAI_sig=18
n_DBHxP_BAI_sig_pos=18-6 #(exceptions: QURU & ACRU at HF, BEPA at NIO, QUVE at SCBI,  ACSA at LDW, AFXY at HKK)
#T:
n_DBHxT_RW_analyzed= 34
n_DBHxT_RW_sig=13
n_DBHxT_RW_sig_neg=5 #notable that it's minority neg for RW, contrasting with slight majority neg for BAI 
n_DBHxT_BAI_analyzed= 35
n_DBHxT_BAI_sig=10
n_DBHxT_BAI_sig_neg=6 #mostly drought signal
```

Interactive effects of climate and $DBH$ were found for `r n_DBHx_analyzed_sig` of the `r n_DBHx_analyzed` (`r round(n_DBHx_analyzed_sig/ n_DBHx_analyzed*100)`%) species-variable combinations for which they could be tested. 
For precipitation variables, interactions were significant for `r round(n_DBHxP_RW_sig/ n_DBHxP_RW_analyzed*100)`% of interactions with $RW$ as the growth metric and for `r round(n_DBHxP_BAI_sig/ n_DBHxP_BAI_analyzed*100)`% with $BAI$ as the growth metric (Table `r interactions_and_year_summaries`).
The majority of these interactions were positive (`r round(n_DBHxP_RW_sig_pos/n_DBHxP_RW_sig*100)`% for $RW$; `r round(n_DBHxP_BAI_sig_pos/n_DBHxP_BAI_sig*100)`% for $BAI$), indicating that larger trees generally respond more positively (or less negatively) to precipitation or its frequency (Fig.  `r interactions_fig`).
Among the exceptions to this pattern (n=`r n_DBHxP_RW_sig-n_DBHxP_RW_sig_pos` for $RW$, `r n_DBHxP_BAI_sig-n_DBHxP_BAI_sig_pos` for $BAI$), only a minority (n=1 for $RW$, 3 for $BAI$) occurred in species responding positively to precipitation in the current growing season.

@@

**figure on climate - DBH interactions? EFFECT SEEMS TO BE FAIRLY STRONG AT LT AND MAYBE SC (NEEDS UPDATING)** (*See [ISSUE #42 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/42)*)

![**Table 2. Summary of climate $\times DBH$ interactions and $year$ effects.**]()

>>>>

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_DBHx_analyzed=202 #n rows in climate_interactions_coefficients, excluding Hansley
n_DBHx_analyzed_sig=84
#precip:
n_DBHxP_RW_analyzed= 35
n_DBHxP_RW_sig=16
n_DBHxP_RW_sig_pos=n_DBHxP_RW_sig-4 #(exceptions: BEAL, TSCA, ACRU at HF, AFXY at HKK*) *pos response to precip in current growing season

n_DBHxP_BAI_analyzed= n_DBHxP_RW_analyzed
n_DBHxP_BAI_sig=15
n_DBHxP_BAI_sig_pos=10 #(exceptions: QURU & ACRU at HF, BEPA at NIO, QUVE at SCBI*,  AFXY at HKK*) *pos response to precip in current growing season
#T:
n_DBHxT_RW_analyzed= 32
n_DBHxT_RW_sig=11
n_DBHxT_RW_sig_neg=5 #notable that it's minority for RW, contrasting with slight majority neg for BAI

n_DBHxT_BAI_analyzed= n_DBHxT_RW_analyzed
n_DBHxT_BAI_sig=13
n_DBHxT_BAI_sig_neg=8 #mostly drought signal, including 4 species at CB
```

Interactive effects of climate and $DBH$ were found for `r n_DBHx_analyzed_sig` of the `r n_DBHx_analyzed` (`r round(n_DBHx_analyzed_sig/ n_DBHx_analyzed*100)`%) species-variable combinations for which they were tested. 
For precipitation variables, interactions were significant for `r round(n_DBHxP_RW_sig/ n_DBHxP_RW_analyzed*100)`% of interactions with $RW$ as the growth metric and for `r round(n_DBHxP_BAI_sig/ n_DBHxP_BAI_analyzed*100)`% with $BAI$ as the growth metric (Table `r interactions_and_year_summaries`).
The majority of these interactions were positive (`r round(n_DBHxP_RW_sig_pos/n_DBHxP_RW_sig*100)`% for $RW$; `r round(n_DBHxP_BAI_sig_pos/n_DBHxP_BAI_sig*100)`% for $BAI$), indicating that larger trees generally respond more positively (or less negatively) to precipitation or its frequency (Fig.  `r interactions_fig`).
Among the exceptions to this pattern (n=`r n_DBHxP_RW_sig-n_DBHxP_RW_sig_pos` for $RW$, `r n_DBHxP_BAI_sig-n_DBHxP_BAI_sig_pos` for $BAI$), only a minority (n=1 for $RW$, 2 for $BAI$) occurred in species responding positively to precipitation in the current growing season.

@@

**figure or table on climate - DBH interactions?** (*See [ISSUE #107 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/107)*)
